Democratizing Secure Two-Party Computation

### 2017-10-15 OaklandSubmission/intro.tex
started to read the paper draft

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community.

@@

Secure multi-party computation \cite{yao,gmw} (SMC) is a powerful cryptographic tool that allows a set of mutually distrusting parties to compute a joint function of their secret inputs. Examples of these include various machine learning prediction algorithm where one party holds the secret input such as a medical report and the other party holds the ML model for disease prediction. Since the introduction of SMC in 1980's, there has been a large body of work \cite{..} that has transformed SMC from a mere theoretical tool to something practically efficient and usable. Hence, there have been efforts to make SMC accessible to non-specialist programmers. To understand the state-of-the-art, let us consider the following toy example.

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options.  
\begin{tiret}
\item He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm,smcl} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes and split the functionality into such parts accordingly. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, the current system of ABY is not suitable to be used by non-specialist programmers.

@@

In this work, we develop and implement our framework \tool \nc{I still like EasyPC :)} \divya{I agree that \tool is bad. What would be the full form for EasyPC? Shouldn't it be EasySC?} for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level \divya{C-like} program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{eval}). Below, we will  give an overview of \tool and describe our contributions in more detail.

@@

\textbf{Programmability.} \tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >b$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like {\tt MULT, ADD, CONS, GT}, etc. The programmer is also required to use the appropriate share conversion gates such as {\tt A2Y} that converts Arithmetic shares to Yao shares. Moreover, it is easy to maintain code in \tool and small change to the functionality requires only a small change in the code. In contrast, working with ABY, even for a small change a developer might have to re-work the whole circuit for efficiency reasons. We describe these examples in detail in \sectionref{ex}.

>>>>

\section{Introduction}
\label{sec:intro}
\aseem{Is the title too general :). May be we want something more
  specific on the lines of A compiler for mixed efficient MPC
  protocols, or something?}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool
support.\aseem{We might want to bring in efficiency in the first
  couple of sentences. Else, we are contradicting the previous two
  sentences below when we say ``He can code up the functionality in a
  programmer friendly DSL''.}
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community.

@@

\aseem{May be it is in transition still ... but the paragraph below
  should be the first paragraph of the paper, else it seems strange to
  introduce SMC after using SMC in the first paragraph? Also, SMC or MPC?}
Secure multi-party computation \cite{yao,gmw} (SMC) is a powerful
cryptographic tool that allows a set of mutually distrusting parties
to compute a joint function of their secret inputs. Examples of these
include various machine learning prediction algorithm where one party
holds the secret input such as a medical report and the other party
holds the ML model for disease prediction. Since the introduction of
SMC in 1980's, there has been a large body of work \cite{..} that has
transformed SMC from a mere theoretical tool to something practically
efficient and usable. Hence, there have been efforts to make SMC
accessible to non-specialist programmers. To understand the
state-of-the-art, let us consider the following toy
example.\aseem{Could we not call it a toy example, and say that this
  computation is part (sub-computation) of some real ML application or
  something?}

Suppose a developer wants to compute $w^Tx >0$ securely using
SMC. With the current techniques, he has two options.\aseem{Nice
  first example.} \aseem{We should
  use she for the programmer instead of he?}
\begin{tiret}
\item He can code up the functionality in a programmer friendly
  domain-specific language such as
  \cite{lambdaps,wysteria,oblivm,smcl} that would automatically
  compile it to an SMC protocol. The downside is that all of these
  works build on a cryptographic back-end that is either entirely
  boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}\aseem{This
    homo citation is broken.}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
\item To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of
complex trade-offs between arithmetic and boolean cryptographic
schemes and split the functionality into such parts accordingly. In
their framework, the programmer is required to write circuits
consisting of  arithmetic and boolean gates along with appropriate
conversion gates. In short, the current system of ABY is not suitable
to be used by non-specialist programmers.\aseem{Doesn't their paper
  itself say that the framework is not programmable and we need
  a high-level language and a compiler for mixed protocols?}

@@

In this work, we develop and implement our framework \tool \nc{I still
  like EasyPC :)} \divya{I agree that \tool is bad. What would be the
  full form for EasyPC? Shouldn't it be EasySC?} for secure
computation that achieves generality, performance and programmer
productivity. The programmer writes a high level \divya{C-like}
program (instead of a circuit) to describe the function to be
computed. Our compiler automatically generates an SMC protocol using a
mix of Arithmetic and Boolean compute. Our compiler is general and can
work with any secure implementation of a mix of arithmetic and boolean
computations. In our work, we focus on semi-honest secure two-party
computation. We build on ABY \cite{aby} that provides the suitable
cryptographic back-end in this setting. We provide a formal type
system and prove correctness and security of our compiler. We evaluate
our system on various benchmarks such as logistic regression and
convolutional neural network (CNN) for MNIST data \cite{minionn},
naive bayes, decision trees from \cite{shafindss}. Evaluations show
that protocols generated by our compiler match (\aseem{or better?})
the performance of hand-crafted protocols in most cases (see
\sectionref{eval}). Below, we will  give an overview of \tool and
describe our contributions in more detail.

@@

\textbf{Programmability.} \tool is a programmer-friendly framework to
express the function to be computed and uses a mix of arithmetic and
boolean SMC back-ends. We illustrate the above toy example of $w^Tx
>b$ in our language in \figureref{ex-sml}.\aseem{Some questions on the
  example, related to initialization, will discuss in tomorrow's
  meeting.} As is clear from the code,
the programmer is not required to write keywords such as {\em secret}
or {\em public} and can remain completely oblivious of the
cryptographic back-end. In contrast, \figureref{ex-aby} illustrates
the same example using the framework in ABY \cite{aby}. Here, as
already mentioned, the programmer needs to write the low level gates
like {\tt MULT, ADD, CONS, GT}, etc. The programmer is also required
to use the appropriate share conversion gates such as {\tt A2Y} that
converts Arithmetic shares to Yao shares. Moreover, it is easy to
maintain code in \tool and small change to the functionality requires
only a small change in the code. In contrast, working with ABY, even
for a small change a developer might have to re-work the whole circuit
for efficiency reasons. We describe these examples in detail in
\sectionref{ex}.
